---
title: "API Introduction"
output: html_notebook
---


## API Packages

```{r}
api_list <- c("httr","jsonlite")
for(i in api_list){
  if(!(i %in% installed.packages())){
    install.packages(i)
  }
}
library(httr)
library(jsonlite)
```

## Types of API Requests
- GET, PUT, and POST (likely more).

## API Requests from RapidAPI
Link: https://rapidapi.com/api-sports/api/api-nba
```{r}
url <- "https://api-nba-v1.p.rapidapi.com/seasons"

api_response <- VERB("GET", url, 
            add_headers('X-RapidAPI-Key' = Sys.getenv('RAPID_API'), 
            'X-RapidAPI-Host' = 'api-nba-v1.p.rapidapi.com'), 
            content_type("application/octet-stream"))
api_response
content(api_response, "text")
```

## WHAT Happens 
      Response [https://api-nba-v1.p.rapidapi.com/seasons]
      Date: 2023-09-04 20:05
      Status: 200
      Content-Type: application/json
      Size: 112 B
- The status of the response should be 200 indicating that the request was successful and a response was generated.
- There should be information on the content type as well.
- A quick preview of the content can be achieved by using the code snippet below and the output is shown for demonstration purposes.

      content(api_response, "text")
      [1] "{\"get\":\"seasons\\/\",\"parameters\":[],\"errors\":[],\"results\":       8,\"response\":[2015,2016,2017,2018,2019,2020,2021,2022]}"

## WHAT to do with the Data
- Original response is raw UNICODE data found in the response list
```{r}
typeof(api_response)
```
## WHAT is a json format?
- The json format which I initially learned about when studying python through the University of Michigan Runestone platform is a format of storing data as key-value pairs often also referred to as the dictionary format.

      {
        "name": "swaggy T"
        "number of years": 32
      }

## How to get to JSON format?
```{r}
rawToChar(api_response$content)
```

- The output here is not a typical looking dictionary or json format, rather a character vector that resembles the JSON format

## How to get usable data

```{r}
nba_data <- fromJSON(rawToChar(api_response$content))
nba_data <- as.data.frame(nba_data$response)
print(nba_data)
```

- Try using the janitor package (perhaps use tidyverse to pipe into clean_names()) to clean the data.
- Did not work for me and likely won't work for you. 

## Conclusions
- Demonstrated the use of R functions httr and jsonlite as clients for APIs hosted by RapidAPI.
- Demonstrated fine skill in observing the output and determining the right subset approach in obtaining desired data from chosen APIs
- Next will be using these APIs to build apps that automatically update data
